---
title: "Journal (reproducible report)"
author: "Bora Lee"
date: "2020-12-02"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    toc_depth: 3
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

**IMPORTANT:** You can delete everything in here and start fresh. You might want to start by not deleting anything above this line until you know what that stuff is doing.

This is an `.Rmd` file. It is plain text with special features. Any time you write just like this, it will be compiled to normal text in the website. If you put a \# in front of your text, it will create a top level-header.

# My first post

Last compiled: `r Sys.Date()`


# Challenge 2

## Challenge 2_1

```{r plot 2_1, fig.width=10, fig.height=7}
memory.limit(size = 100000)

### Challenge 2_1
library(tidyverse)
library(readxl)
library(lubridate)
bikes_tbl <- read_excel("D:/3rd semester/Data_Science_Business/Data_science_Basic/DS_101/DS_101/00_data/01_bike_sales/01_raw_data/bikes.xlsx")
orderlines_tbl <- read_excel("D:/3rd semester/Data_Science_Business/Data_science_Basic/DS_101/DS_101/00_data/01_bike_sales/01_raw_data/orderlines.xlsx")
bikeshops_tbl <- read_excel("D:/3rd semester/Data_Science_Business/Data_science_Basic/DS_101/DS_101/00_data/01_bike_sales/01_raw_data/bikeshops.xlsx")


# Chaining commands with the pipe and assigning it to order_items_joined_tbl
bike_orderlines_joined_tbl <- orderlines_tbl %>%
  left_join(bikes_tbl, by = c("product.id" = "bike.id")) %>%
  left_join(bikeshops_tbl, by = c("customer.id" = "bikeshop.id"))


bike_orderlines_wrangled_tbl <- bike_orderlines_joined_tbl %>%
  separate(col    = category,
           into   = c("category.1", "category.2", "category.3"),
           sep    = " - ") %>%
  mutate(total.price = price * quantity) %>%
  select(-...1, -gender) %>%
  select(-ends_with(".id")) %>%
  bind_cols(bike_orderlines_joined_tbl %>% select(order.id)) %>% 
  select(order.id, contains("order"), contains("model"), contains("category"),
         price, quantity, total.price,
         everything()) %>%
  rename(bikeshop = name) %>%
  set_names(names(.) %>% str_replace_all("\\.", "_"))


sales_by_loc_tbl <- bike_orderlines_wrangled_tbl %>%
  separate(col = location, into = c("city","state"), sep = ",") %>% 
  group_by(state) %>% 
  select(city, state, total_price, quantity) %>% 
  summarize(total_sales = sum(quantity), 
            total_revenue = sum(total_price)) %>% 
  mutate(revenue_text = scales::dollar(total_revenue, 
                                       big.mark=".",
                                       decimal.mark=",",
                                       prefix=" ",
                                       suffix ="€"))

sales_by_loc_tbl %>% 
  ggplot(aes(x = state, y = total_sales)) +
       theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  geom_col(fill = "#2DC6D6")+
  geom_label(aes(label = revenue_text))+
  geom_smooth(method = "loess", se = FALSE)+
  scale_y_continuous(labels = scales::dollar_format(big.mark=".",
                                                    decimal.mark = ",",
                                                    prefix = "",
                                                    suffix = "€")) +
  labs(title = "Revenue by State",
       x = "",
       y = "Total_Revenue") 
  
```
## Challenge 2_2

```{r plot 2_2, fig.width=10, fig.height=7}
sales_year_state_tbl <- bike_orderlines_wrangled_tbl %>% 
  separate(col = location, into = c("city","state"), sep = ",") %>% 
  mutate(year = year(order_date)) %>% 
  select(year, city, state, total_price, quantity) %>% 
  group_by(year, state) %>% 
  summarise(total_sales = sum(quantity), total_revenue = sum(total_price)) %>%
  ungroup() %>%
  mutate(revenue_text = scales::dollar(total_revenue, big.mark = ".",decimal.mark = ",",  prefix = "", suffix = " €"))
 
# plotting                                                                             
sales_year_state_tbl %>% 
  ggplot(aes(x = year, y = total_revenue, fill = state)) + geom_col() +  
  facet_wrap(~ state) +
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "",  
                                                    suffix = " €")) +
  labs( title = "Revenue by State", 
        x = "", 
        y = "Revenue" )


```
# Challenge 3

## Challenge 3_2

```{r, eval=FALSE}

library(jsonlite)
library(httr)
library(glue)
library(magrittr)
library(rvest)
library(stringr)
library(tidyverse)
library(purrr)

#install.packages("rstudioapi")
library("rstudioapi")


token <- "uju"
#url_3 <- "https://www.youtube.com/channel/UCB9IPcQ_x8dO66s1Y9FZUDg"
url_3 <- "https://www.skyscanner.co.kr/transport/flights/ham/lju/201217/201222/?adultsv2=1&cabinclass=economy&childrenv2=&inboundaltsenabled=false&outboundaltsenabled=false&preferdirects=false&priceSourceId=&priceTrace=202011242052*I*HAM*LJU*20201217*luft*LH%7C202011242052*I*LJU*HAM*20201222*luft*LH&qp_prevCurrency=EUR&qp_prevPrice=184&qp_prevProvider=ins_month&rtn=1"
resp <- GET(url_3, query = list("function" = "GLOBAL_QUOTE",
        
                        apikey = askForPassword(token))
)

challenge_3_1 <- resp %>%
  .$content %>% 
  rawToChar() %>% 
  fromJSON()

print(challenge_3_1)
```

## Challenge 3_2
```{r}
library(jsonlite)
library(httr)
library(glue)
library(magrittr)
library(rvest)
library(stringr)
library(tidyverse)
library(purrr)

ebike1 <- "https://www.radon-bikes.de/mountainbike/hardtail/"
ebike2 <- "https://www.radon-bikes.de/mountainbike/fullsuspension/"

ebike <- c(ebike1, ebike2)
get_bike_data_c <- function(url) {
  html_category <- read_html(url)
  
  
  
  wheel_size_tbl <- html_category %>% 
    html_nodes(css = ".wheelSizes .a-parallelogram") %>% 
    html_text()%>% stringr::str_extract(pattern = "[0-9]+") %>% 
    as.numeric() %>% enframe(name = "position", value="wheel_size")
  bike_subtitle_tbl <- html_category %>% 
    html_nodes(css = ".bikeTitle .subtitle") %>% 
    html_text() %>% 
    enframe(name = "position", value="subtitle")
  bike_price_tbl <- html_category %>% 
    html_nodes(css = ".currency_eur .currentPrice") %>% 
    html_text()%>% 
    stringr::str_extract(pattern = "[0-9]+")  %>% 
    as.numeric() %>% 
    enframe(name = "position", value="price_euro")
  bike_title_tbl <- html_category %>% 
    html_nodes(css = ".bikeTitle >h4") %>% 
    html_text() %>% as_tibble() %>% 
    rowid_to_column(var='position') %>%
    left_join(bike_subtitle_tbl) %>%
    left_join(bike_price_tbl) %>%
    left_join(wheel_size_tbl) %>% 
    rename(Title = "value") 
  
}

Challenge3_a <- get_bike_data_c(ebike[1])
Challenge3_b <- get_bike_data_c(ebike[2])
challenge3_2 <- bind_rows(Challenge3_a, Challenge3_b)
challenge3_2


print(challenge3_2)
```

# Challenge 4
## Challenge 4_1

```{r}

library(tidyverse)
library(vroom)
library(data.table)
library(lubridate)
library(dplyr)

col_types <- list(
  id = col_character(),
  type = col_double(),
  organization = col_character()
)
    
assignee_tbl_row <- vroom(
  file       = "C:/Users/ybora/Desktop/Patent_data_reduced/assignee.tsv", 
  delim      = "\t", 
  col_types  = col_types,
  na         = c("", "NA", "NULL")
)


col_types <- list(
  patent_id = col_character(),
  assignee_id = col_character()

)              
patent_as_tbl_row <- vroom(
  file       = "C:/Users/ybora/Desktop/Patent_data_reduced/patent_assignee.tsv", 
  delim      = "\t", 
  col_types  = col_types,
  na         = c("", "NA", "NULL")
)

col_types <- list(
  id = col_character(),
  date = col_date("%Y-%m-%d"),
  num_claims = col_double()
)

patent_tbl_row <- vroom(
   file       = "C:/Users/ybora/Desktop/Patent_data_reduced/patent.tsv", 
   delim      = "\t", 
   col_types  = col_types,
   na         = c("", "NA", "NULL")
 )

col_types <- list( 
  patent_id = col_character(),
  mainclass_id = col_character(),
  sequence = col_double()
  )
uspc_tbl <- vroom(
     file       = "C:/Users/ybora/Desktop/Patent_data_reduced/uspc.tsv", 
     delim      = "\t", 
     col_types  = col_types,
     na         = c("", "NA", "NULL")
   )

assignee_tbl <- assignee_tbl_row %>% select(id, organization, type) %>% filter(type == 2) %>% filter(!is.na(organization)) %>% rename(assignee_id = "id")
patent_as_tbl <- patent_as_tbl_row %>% select(assignee_id, patent_id) %>% left_join(assignee_tbl, by="assignee_id")

challenge_1 <- patent_as_tbl %>%  filter(!is.na(organization)) %>% select(organization, patent_id) %>% group_by(organization) %>% summarise(number_patent = n()) 
challenge_1 <- challenge_1 %>% arrange(desc(number_patent)) %>% filter(!is.na(organization))
challenge_1_10 <- challenge_1 %>% head(n=10)
print(challenge_1_10)

```


## Challenge 4_2

```{r}

patent_tbl <- patent_tbl_row %>% select(id, date) %>% rename(patent_id = "id")
patent_tbl$month <- as.numeric(format(patent_tbl$date, "%m"))
patent_tbl_y <- patent_tbl %>% filter(month == 1) %>% select(-date)

challenge_2 <- patent_tbl_y %>% left_join(patent_as_tbl, by="patent_id")
challenge_2 <- challenge_2 %>% filter(!is.na(type)) %>% filter(!is.na(organization))
challenge_2_f <- challenge_2 %>% select(organization, patent_id) %>% group_by(organization) %>% summarise(number_patent = n()) 
challenge_2_f <- challenge_2_f %>% arrange(desc(number_patent)) %>% filter(!is.na(organization)) %>% head(n=10)
print(challenge_2_f)


```



# Challenge 5
## Challenge 5_1
```{r plot 5_1, fig.width=10, fig.height=7}
## challenge 5
library(tidyverse)
library(devtools)
library(ggplot2)
library(ggmap)
library(maps)
library(mapdata)


covid_data_tbl <- read_csv("https://opendata.ecdc.europa.eu/covid19/casedistribution/csv")

#challenge 5_1
cd_europe <- covid_data_tbl %>% 
  filter(continentExp == "Europe") %>% 
  filter(year == 2020) %>%
  select(year, month, day, cases)


cd_europe_cum <- cd_europe %>% 
  mutate(date = 
           as.Date(with(cd_europe, paste(year, month, day, sep="-")), 
                   "%Y-%m-%d")) %>%
  group_by(date) %>%
  summarise(cases = sum(cases)) %>%
  ungroup() %>%
  arrange(date = as.Date(date, "%d-%m-%Y")) %>%
  mutate(cum_cases = cumsum(cases))

cd_diverse <- covid_data_tbl %>% 
  filter(countriesAndTerritories %in% 
           c("Germany","United_Kingdom","France",
             "Spain","United_States_of_America" ))  %>% 
  filter(year == 2020) %>%
  select(year, month, day, cases, countriesAndTerritories) 

cd_diverse_cum <- cd_diverse %>% 
  mutate(date = 
           as.Date(with(cd_diverse, paste(year, month, day, sep="-")), 
                   "%Y-%m-%d")) %>%
  select(countriesAndTerritories, date, cases) %>%
  arrange(date = as.Date(date, "%d-%m-%Y")) %>%
  group_by(countriesAndTerritories) %>%
  mutate(cum_cases = cumsum(cases)) 

cd_europe_cum <- cd_europe_cum %>% 
  mutate(countriesAndTerritories = "Europe")
combined <- cd_europe_cum %>%  bind_rows(cd_diverse_cum) 
#why is there NA? 
combined_w <- 
  pivot_wider(combined, names_from = "countriesAndTerritories", values_from = "cum_cases") 

bb <- combined %>% 
  filter(countriesAndTerritories == "Europe") %>% 
  select(countriesAndTerritories, cum_cases)
bb2 <- bb$cum_cases[332]


combined %>% 
  ggplot(aes(x=date, y=cum_cases, color = countriesAndTerritories)) +
  geom_line(size = 1) +
  scale_y_continuous(
    labels = scales::dollar_format(scale = 1e-6, prefix = "",suffix = "M", 
                                   decimal.mark = ","))+
  labs(
    title = "Covid-19 confirmed cases worldwide",
    subtitle = "As of 11/27/2020, Europe had more cases than the USA" ,
    x = "Year 2020", y = "Cumulative Cases" , color = "Continent/Country"
  ) +
  theme(
    panel.background = element_rect(fill= "black"),
    panel.border = element_rect(fill=NA),
    panel.grid = element_line(color = "white"),
    legend.position = "bottom",
  ) 

```

## Challenge 5_2
```{r plot 5_2, fig.width=10, fig.height=7}
## challenge 5_2
memory.limit(size = 1000000)
library(readxl)


covid_death <- covid_data_tbl %>%
  filter(year == 2020) %>%
  select(countriesAndTerritories, deaths, popData2019) %>%
  mutate(across(countriesAndTerritories, str_replace_all, "_", " ")) %>%
  mutate(countriesAndTerritories = case_when(
    
    countriesAndTerritories == "United Kingdom" ~ "UK",
    countriesAndTerritories == "United States of America" ~ "USA",
    countriesAndTerritories == "Czechia" ~ "Czech Republic",
    TRUE ~ countriesAndTerritories
   )) %>%
  mutate(country = countriesAndTerritories) %>%
  mutate(population = popData2019) %>%
  select(country, deaths, population) %>%
  group_by(country) %>%
  summarise(sum_death = sum(deaths),
            mortality_rate = sum_death/population) %>%
  ungroup() %>%
  distinct()





world <- map_data("world")

world_tbl <- as_tibble(world) %>% mutate(country = region) %>%
  select(long, lat, country)
world_data_2<- covid_death %>% 
  select(country, mortality_rate) %>%
  left_join(world_tbl, by = "country") %>% distinct()

world_data_2 %>% ggplot(aes(x = long, y= lat, fill = mortality_rate))+
  geom_map(aes(map_id = country),
           map = world
               ) +
  labs(
    title = "Confirmed COVID-19 deaths relative to the size of the population",
    subtitle = "More than 1.2 Million confirmed COVID-19 deaths worldwide",
    caption = "Date: 11/27/2020",
    x = "", y = ""
  ) +
  scale_fill_continuous(
    labels = scales::dollar_format
    (scale = 10^2, prefix = "",
      suffix = "%", decimal.mark = "."))+
  theme(
    #panel.background = element_rect(fill= "black"),
    panel.border = element_rect(fill=NA),
    panel.grid = element_line(color = "white"),
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.x = element_blank(),
    axis.ticks.y = element_blank()
  )

```

## Second level header

You can add more headers by adding more hashtags. These won't be put into the table of contents

### third level header

Here's an even lower level header

# My second post (note the order)

Last compiled: `r Sys.Date()`

I'm writing this tutorial going from the top down. And, this is how it will be printed. So, notice the second post is second in the list. If you want your most recent post to be at the top, then make a new post starting at the top. If you want the oldest first, do, then keep adding to the bottom

# Adding R stuff

So far this is just a blog where you can write in plain text and serve your writing to a webpage. One of the main purposes of this lab journal is to record your progress learning R. The reason I am asking you to use this process is because you can both make a website, and a lab journal, and learn R all in R-studio. This makes everything really convenient and in the same place. 

So, let's say you are learning how to make a histogram in R. For example, maybe you want to sample 100 numbers from a normal distribution with mean = 0, and standard deviation = 1, and then you want to plot a histogram. You can do this right here by using an r code block, like this:

